Checkpoint 4

### 2020-04-28 Checkpoint 4.Rmd
trying some models

```{r, warning=FALSE}
library(dplyr)
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)
library(rgdal)
library(gridExtra)
library(plotly)
require(janitor)
require(reshape2)
require(tidyr)
require(rstan)
require(rstanarm)
require(bayesplot)
```

@@

ggplotly(a)
ggplotly(b)
ggplotly(c) #Shows that Democrat states tend to have a higher interest in Googling China Virus 
ggplotly(d)
```

>>>>

```{r, warning=FALSE, include=FALSE}
library(dplyr)
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)
library(rgdal)
library(gridExtra)
library(plotly)
require(janitor)
require(reshape2)
require(tidyr)
require(rstan)
require(rstanarm)
require(bayesplot)
```

```{r}
Finaldata<-read.csv("time_series_final_Data.csv")
```

```{r} 
Finaldata <- Finaldata %>% select(-c(X)) 
Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
names(Finaldata)
```

```{r}
Finaldata%>%
  mutate(perc_population_positive = positive/total_population)%>%
  group_by(State)%>%
  mutate(mean_corona_interest = mean(ChinaVirusInterest),
         max = max(ChinaVirusInterest),
         median = median(ChinaVirusInterest))%>%
  ggplot(aes(x = mean_corona_interest, y = perc_population_positive, color = percent_asian))+
  geom_point()+
  scale_colour_gradient2(low = "blue", mid = "lightblue", high = "red")
```

@@

ggplotly(a)
ggplotly(b)
ggplotly(c) #Shows that Democrat states tend to have a higher interest in Googling China Virus 
ggplotly(d)

# What affects the China Interest search, is it demographic, policitical or COVID based? 
## From Alicia:: Start by thinking, take the four models from the sleep study and just think how we can go thorugh those four models in the context of our work. It's
```

```{r}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

model_1 <- stan_glmer(
  ChinaVirusInterest ~ (1 | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

```{r}
model_2 <- stan_glmer(
  ChinaVirusInterest ~ Day + (Day | State),
  data = Finaldata, family = gaussian,
  chains = 4, iter = 5000*2, refresh = 0
)

```

```{r}
# model_3 <- stan_glmer(
#   ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
#   data = Finaldata, family = gaussian,
#   chains = 4, iter = 100, refresh = 0
# )
```

```{r}
# model_4 <- stan_glm(
#   Reaction ~ 1,
#   data = sleep, family = gaussian,
#   chains = 4, iter = 5000*2
# )
# 
```

```{r}
head(data.frame(summary(model_1)),-2)
```
